High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
robustnn not as good as expected unfortunately

	front = Flux.Chain(
        Conv((k, k), 1 => c1, pad=(p, p), relu),
        MaxPool((2, 2)),
        Conv((k, k), c1 => c2, pad=(p, p), relu),
        MaxPool((2, 2)),
        Flux.flatten
    )
	d = Flux.outputsize(front, (_n_in, _n_in, 1, 1)) |> first
    back = Flux.Chain(
        Dense(d, 120, relu),
        Dense(120, 84, relu),
        Dense(84, n_out),
    )

@@

add_models = Dict(
    "LeNet-5" => lenet,
    "RobustNet" => rob_net,
    "Large Ensemble (n=50)" => mlp_large_ens,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "RobustNet",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
    plot_factual = true,
    img_height = 150,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

@@

for (factual, target) in combos
    plt, _, _ = _plot_eccco_mnist(
        plt_order = _plt_order,
        model_dict = large_model_dict,
        x = factual,
        target = target,
        wide = true,
        plot_factual = true,
        img_height = 150
    )
    display(plt)
    push!(plts, plt)
end
```

>>>>

	front = Flux.Chain(
        Conv((k, k), 1 => c1, pad=(p, p), sigmoid),
        MaxPool((2, 2)),
        Conv((k, k), c1 => c2, pad=(p, p), sigmoid),
        MaxPool((2, 2)),
        Flux.flatten
    )
	d = Flux.outputsize(front, (_n_in, _n_in, 1, 1)) |> first
    back = Flux.Chain(
        Dense(d, 120, sigmoid),
        Dense(120, 84, sigmoid),
        Dense(84, n_out),
    )

@@

# CNN Ensemble:
lenet_ens = EnsembleModel(model=lenet, n=5)

add_models = Dict(
    "LeNet-5" => lenet,
    "LeNet-5 Ensemble" => lenet_ens,
    # "RobustNet" => rob_net,
    "Large Ensemble (n=50)" => mlp_large_ens,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "LeNet-5 Ensemble",
    # "RobustNet",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
    plot_factual = true,
    img_height = 150,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

@@

for (factual, target) in combos
    plt, _, _ = _plot_eccco_mnist(
        factual, target; 
        plt_order = _plt_order,
        model_dict = large_model_dict,
        wide = true,
        plot_factual = true,
        img_height = 150
    )
    display(plt)
    push!(plts, plt)
end
```
